New_Data_Coherence

### 2019-10-13 Analysis/04_Coherence_Calculations.Rmd
permutation p values
Fix Attention deficit hyperactivity disorder that was run twice

#String
string_p = readRDS("./data/Permutation_Results/string_p_1k.rds") %>% as.data.frame(.)  %>% dplyr::select(-new_coherence)

@@

>>>>

#String
string_p = readRDS("./data/Permutation_Results/Complete_10k_String.rds") %>% as.data.frame(.)  %>% dplyr::select(-new_coherence)
string_p <- string_p[!duplicated(string_p$Disease), ] # Fix "Attention deficit hyperactivity disorder" that was run twice

@@

```{r}
```
